---
title: "Data_Retrieval"
author: "Lake Vitton"
date: "6/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(XML)
library(rvest)
library(stringi)
library(plyr)
library(caret)
library(gmodels)

```

Future Analysis and Model Critique:

In looking back on our approach to this project, there is an issue with the data we are pulling to run our analysis. Specifically, we are pulling the aggregated player stats for YTD and using those to calculate their respective matches. This doesn't allow the models to take into consideration how one loss or win and the player's data from that match would affect their aggreatd YTD stats. This means that some players are being given a statisitical advantage or disadvantage at certain points in their seasons if they had better or worse stats for a period than the overall aggregate.

In order to adjust for this in the future, the model should seek to pull individual match statistics and use them instead of the YTD aggregate, which mitigates the statistical bias described above. This would require modifying the web scraper to search through individual matches. We didn't incorporate this from the beginning because the URL notation does not seem to follow a pattern. To make it work, we will have to pull all matches for top 100 players (or whatever group we want), slice a portion of the URL, and then iterate through that list. Much in the same way we currently do with player codes and player stats. However, this approach is only good for prediciting past matches when we have the actual stats. In order to predict matches in the future we will need to build a moving average for players that only takes their stats from the past n matches and uses that average as the stat to feed the model for future games. We believe that this approach has the potential to increase our accuracy rate of our voting system model. Additionally, the incorporation of an SVM and KNN model will be considered when we have the updated data. 

Through this project, we gained experience in webscraping through R and realized the real-life applications of the concepts taught in TO414. (aka, we can make money now!) 


Now lets make those changes! First we're going to make a new code list to change our approach of getting tournament codes vs going through players
```{r}
tournamenturl <- "http://www.atpworldtour.com/en/tournaments"
tournament_webpage <- read_html(tournamenturl)

#First create a dataframe with all the Tournament Names
TournamentName_HTML <- html_nodes(tournament_webpage,".tourney-title")
TournamentName_text <- html_text(TournamentName_HTML)

#Now we need to know the number of players entered in each tournament, the risk with this is that if the number of 
#players changes year to year there might be quite a few matches that don't have records, we shall see
TournamentPlayerNum_HTML <- html_nodes(tournament_webpage,"a:nth-child(1) .item-value")
TournamentPlayerNum_text <- html_text(TournamentPlayerNum_HTML)

#we also need the surface of the tournament so we can segment later

TournamentSurface_HTML <- html_nodes(tournament_webpage,".tourney-details:nth-child(2) .item-details")
TournamentSurface_text <- html_text(TournamentSurface_HTML)

TournamentCodes <- data.frame(TournamentName = TournamentName_text)
TournamentCodes$PlayerNum <- TournamentPlayerNum_text
TournamentCodes$Link <- 0
TournamentCodes$Surface <- TournamentSurface_text

#get rid of Davis Cup data
Davis <- c(7,22,56,72)
TournamentCodes$TournamentName[Davis] <- "NA"

TournamentCodes <- na.omit(TournamentCodes)

#now look for the links
nodes <- html_nodes(tournament_webpage,"tbody")

LinksList <- html_nodes(nodes, "a")

#iterate through list, just looking for singles, it goes doubles then singles in the list of links
for (x in 1:nrow(TournamentCodes)){
  t3 <- html_attr(LinksList[(x*2-1)][1],"href")
  TournamentCodes$Link[x] <- t3
}

#extract code from Link
TournamentCodes$TournamentCode <- 0

library(tidyverse)

rel <- "\\d\\d\\d\\d|\\d\\d\\d"
Code <- str_extract(TournamentCodes$Link,rel)
TournamentCodes$TournamentCode <- Code

TournamentCodes <- subset(TournamentCodes, !is.na(TournamentCodes$TournamentCode))

```

Ok so in this block below we're looking to generate the tournament and match part of every url so 580/MS127

```{r}
MatchCodes <- NULL

getcode <- function(x){
  return(paste(x,"/MS",sep = ""))
}

result <- mapply(getcode, TournamentCodes$TournamentCode)
MatchCodes = plyr::ldply(result, rbind)
names(MatchCodes) <- c("Tournament","part1")

####### everything aboves here makes the 580/MS


Codes <- NULL
list <- NULL
list <- c(1:127)
list <- stringr::str_pad(list, 3, side = "left", pad = 0)

Result <- c() 

Retrieve <- function(x){
    for(y in list){
      Result <- c(Result, paste(x,y,sep = ""))
    }
  return(Result)
}
list2 <- MatchCodes$part1

Codes <- Retrieve(list2)

```

Now that we have the list of tournament codes and the number of singles entries per tournament we can attempt to scrape individual match stat data from all of them. This will need to look like the PlayerCombinedStats page. 

```{r}
#Get Match Data and stats of players on a match basis

getmatchdata <- function(x) {
  year <- 2017
  matchpage <- paste0("http://www.atpworldtour.com/en/scores/",year,"/",x,"/match-stats")
  match_webpage <- read_html(matchpage)
  
  
  TournamentCode <- paste(substring(x,1,nchar(x)-6))
  
  MatchCode <- x
  
  P1FirstName_HTML <- html_nodes(match_webpage,".player-left-name .first-name")
  P1FirstName_text <- html_text(P1FirstName_HTML)
    
  P1LastName_HTML <- html_nodes(match_webpage,".player-left-name .last-name")
  P1LastName_text <- html_text(P1LastName_HTML)
  
  P1Name <- paste(P1FirstName_text,P1LastName_text)
  
  URL_start <- "https://www.atpworldtour.com"
  s = html_session(URL_start)
  P1URL_HTML <- html_nodes(match_webpage, ".player-left-name a")%>% html_attr("href")
  P1URL_FINAL <- paste(URL_start, P1URL_HTML, sep = "")
  print(P1URL_FINAL)
  P1Page <- read_html(P1URL_FINAL)
  P1 <- html_nodes(P1Page, ".table-big-value")
  p1Age <- P1[1] %>% html_text(trim= TRUE)
  p1Age <- gsub("\r|\n", "", p1Age)
  p1Age<- gsub("\\s+", " ", trimws(p1Age))
  words <- strsplit(p1Age, " ")
  p1AgeFinal <- words[1]
  P1weight <- P1[3] %>% html_text(trim=TRUE)
  print(P1weight)
  P1secondRow <- html_nodes(P1Page, ".table-value")
  P1stance <- P1secondRow[3] %>% html_text(trim=TRUE)
  print(P1stance)
  
  P2URL_HTML <- html_nodes(match_webpage, ".player-right-name a") %>% html_attr("href")
  P2URL_FINAL <- paste(URL_start, P2URL_HTML, sep = "")
  P2Page <- read_html(P2URL_FINAL)
  P2 <- html_nodes(P1Page,  "table-big-value")
  P2Age <- P2[1] %>% html_text(trim=TRUE)
  P2Age <- gsub("\r|\n", "", P2Age)
  P2Age <- gsub("\\s+", " ", trimws(P2Age))
  words2 <- strsplit(P2Age, " ")
  p2AgeFinal <- words2[1]
  P2weight <- P2[3] %>% html_text(trim=TRUE)
  P2secondRow <- html_nodes(P2Page, ".table-value")
  P2stance <- P2secondRow[3] %>% html_text(trim=TRUE)
  
  P2FirstName_HTML <- html_nodes(match_webpage,".player-right-name .first-name")
  P2FirstName_text <- html_text(P2FirstName_HTML)
  
  #we need to bring this in later so we can deal with score  
  P2LastName_HTML <- html_nodes(match_webpage,".player-right-name .last-name")
  P2LastName_text <- html_text(P2LastName_HTML)
  
  P2Name <- paste(P2FirstName_text,P2LastName_text)
  
  #Data not in the match page, must be retrieves from PlayerData
  #Birthday_HTML <- html_nodes(player_webpage,".table-birthday-wrapper")
  #Birthday_text <- html_text(Birthday_HTML)
  
  #Weight_HTML <- html_nodes(player_webpage,".table-weight-kg")
  #Weight_text <- html_text(Weight_HTML)
    
  #Height_HTML <- html_nodes(player_webpage,".table-height-cm-wrapper")
  #Height_text <- html_text(Height_HTML)
    
  #Stance_HTML <- html_nodes(player_webpage,"td:nth-child(3) .table-value")
  #Stance_text <- html_text(Stance_HTML)
    

#Service Stats Below
  #Serve Rating
  P1ServeRating_HTML <- html_nodes(match_webpage,".percent-on:nth-child(2) .match-stats-number-left a")
  P1ServeRating_text <- html_text(P1ServeRating_HTML)
  
  P2ServeRating_HTML <- html_nodes(match_webpage,".percent-on:nth-child(2) .match-stats-number-right a")
  P2ServeRating_text <- html_text(P2ServeRating_HTML)

  #Aces
  P1Aces_HTML <- html_nodes(match_webpage,".percent-on:nth-child(3) .match-stats-number-left span")
  P1Aces_text <- html_text(P1Aces_HTML)
  
  P2Aces_HTML <- html_nodes(match_webpage,".percent-on:nth-child(3) .match-stats-number-right span")
  P2Aces_text <- html_text(P2Aces_HTML)
  #DeltaAces <- P1Aces_text - P2Aces_text

  #Double Faults
  P1DoubeFaults_HTML <- html_nodes(match_webpage,".percent-on:nth-child(4) .match-stats-number-left span")
  P1DoubeFaults_text <- html_text(P1DoubeFaults_HTML)
  
  P2DoubeFaults_HTML <- html_nodes(match_webpage,".percent-on:nth-child(4) .match-stats-number-right span")
  P2DoubeFaults_text <- html_text(P2DoubeFaults_HTML)

  #1st Serve
  P1FirstServe_HTML <- html_nodes(match_webpage,".percent-on:nth-child(5) .match-stats-number-left span:nth-child(1)")
  P1FirstServe_text <- html_text(P1FirstServe_HTML)
  
  P2FirstServe_HTML <- html_nodes(match_webpage,".percent-on:nth-child(5) .match-stats-number-right span:nth-child(1)")
  P2FirstServe_text <- html_text(P2FirstServe_HTML)

  #1st Serve Points Won
  P1FirstServePtsWon_HTML <- html_nodes(match_webpage,".percent-on:nth-child(6) .match-stats-number-left span:nth-child(1)")
  P1FirstServePtsWon_text <- html_text(P1FirstServePtsWon_HTML)
  
  P2FirstServePtsWon_HTML <- html_nodes(match_webpage,".percent-on:nth-child(6) .match-stats-number-right span:nth-child(1)")
  P2FirstServePtsWon_text <- html_text(P2FirstServePtsWon_HTML)

  #2nd Serve Points Won
  P1SecServePtsWon_HTML <- html_nodes(match_webpage,".percent-on:nth-child(7) .match-stats-number-left span:nth-child(1)")
  P1SecServePtsWon_text <- html_text(P1SecServePtsWon_HTML)
  
  P2SecServePtsWon_HTML <- html_nodes(match_webpage,".percent-on:nth-child(7) .match-stats-number-right span:nth-child(1)")
  P2SecServePtsWon_text <- html_text(P2SecServePtsWon_HTML)

  #Break Points Saved
  P1ServeRating_HTML <- html_nodes(match_webpage,".percent-on:nth-child(2) .match-stats-number-left a")
  P1ServeRating_text <- html_text(P1ServeRating_HTML)
  
  P2ServeRating_HTML <- html_nodes(match_webpage,".percent-on:nth-child(2) .match-stats-number-right a")
  P2ServeRating_text <- html_text(P2ServeRating_HTML)

  #Service Games Played
  P1ServiceGamessPlayed_HTML <- html_nodes(match_webpage,".percent-on:nth-child(8) .match-stats-number-left span:nth-child(1)")
  P1ServiceGamessPlayed_text <- html_text(P1ServiceGamessPlayed_HTML)
  
  P2ServiceGamessPlayed_HTML <- html_nodes(match_webpage,".percent-on:nth-child(8) .match-stats-number-right span:nth-child(1)")
  P2ServiceGamessPlayed_text <- html_text(P2ServiceGamessPlayed_HTML)

#Return Stats Below

  #Return Rating		
  P1ReturnRating_HTML <- html_nodes(match_webpage,".percent-on~ .percent-on .match-stats-number-left a")
  P1ReturnRating_text <- html_text(P1ReturnRating_HTML)
  
  P2ReturnRating_HTML <- html_nodes(match_webpage,".percent-on~ .percent-on .match-stats-number-right a")
  P2ReturnRating_text <- html_text(P2ReturnRating_HTML)

  #1st Serve Return Points Won	
  P1FirstServeReturnPointsWon_HTML <- html_nodes(match_webpage,".percent-on:nth-child(12) .match-stats-number-left span:nth-child(1)")
  P1FirstServeReturnPointsWon_text <- html_text(P1FirstServeReturnPointsWon_HTML)
  
  P2FirstServeReturnPointsWon_HTML <- html_nodes(match_webpage,".percent-on:nth-child(12) .match-stats-number-right span:nth-child(1)")
  P2FirstServeReturnPointsWon_text <- html_text(P2FirstServeReturnPointsWon_HTML)

  #2nd Serve Return Points Won
  P1SecondServeReturnPointsWon_HTML <- html_nodes(match_webpage,".percent-on:nth-child(13) .match-stats-number-left span:nth-child(1)")
  P1SecondServeReturnPointsWon_text <- html_text(P1SecondServeReturnPointsWon_HTML)
  
  P2SecondServeReturnPointsWon_HTML <- html_nodes(match_webpage,".percent-on:nth-child(13) .match-stats-number-right span:nth-child(1)")
  P2SecondServeReturnPointsWon_text <- html_text(P2SecondServeReturnPointsWon_HTML)

  #Break Points Converted		
  P1BreakPointsConverted_HTML <- html_nodes(match_webpage,".percent-on:nth-child(14) .match-stats-number-left span:nth-child(1)")
  P1BreakPointsConverted_text <- html_text(P1BreakPointsConverted_HTML)
  
  P2BreakPointsConverted_HTML <- html_nodes(match_webpage,".percent-on:nth-child(14) .match-stats-number-right span:nth-child(1)")
  P2BreakPointsConverted_text <- html_text(P2BreakPointsConverted_HTML)

#Point Stats Below

  #Service Points Won	
  P1ServicePtsWon_HTML <- html_nodes(match_webpage,".percent-on:nth-child(17) .match-stats-number-left span:nth-child(1)")
  P1ServicePtsWon_text <- html_text(P1ServicePtsWon_HTML)
  
  P2ServicePtsWon_HTML <- html_nodes(match_webpage,".percent-on:nth-child(17) .match-stats-number-right span:nth-child(1)")
  P2ServicePtsWon_text <- html_text(P2ServicePtsWon_HTML)

  #Return Points Won	
  P1ReturnPtsWon_HTML <- html_nodes(match_webpage,".percent-on:nth-child(18) .match-stats-number-left span:nth-child(1)")
  P1ReturnPtsWon_text <- html_text(P1ReturnPtsWon_HTML)
  
  P2ReturnPtsWon_HTML <- html_nodes(match_webpage,".percent-on:nth-child(18) .match-stats-number-right span:nth-child(1)")
  P2ReturnPtsWon_text <- html_text(P2ReturnPtsWon_HTML)

  
 return(t(c(TournamentCode,MatchCode,P1Name, P2Name,P1ServeRating_text,P2ServeRating_text,P1Aces_text,P2Aces_text,P1DoubeFaults_text,P2DoubeFaults_text,P1FirstServe_text,P2FirstServe_text,P1FirstServePtsWon_text,P2FirstServePtsWon_text,P1SecServePtsWon_text,P2SecServePtsWon_text,P1BreakPointsConverted_text,P2BreakPointsConverted_text,P1ServicePtsWon_text,P2ServicePtsWon_text,P1ReturnPtsWon_text,P2ReturnPtsWon_text)))

}

result = lapply(Codes[1:10],getmatchdata)
#result = lapply(Codes[1:8382],getmatchdata)
MatchData = plyr::ldply(result, rbind)

names(MatchData) <- c("TournamentCode","MatchCode","P1Name","P2Name","P1ServeRating","P2ServeRating","P1Aces","P2Aces","P1DoubleFaults","P2DoubleFaults","P1FirstServe","P2FirstServe","P1FirstServePtsWon","P2FirstServePtsWon","P1SecServePtsWon","P2SecServePtsWon","P1BreakPointsConverted","P2BreakPointsConverted","P1ServicePtsWon","P2ServicePtsWon","P1ReturnPtsWon","P2ReturnPtsWon")

#add in the tournament name and surface type using leftjoin
MatchData <- left_join(MatchData,TournamentCodes[1:20,], by = c("TournamentCode"))
MatchData$TournamentName <- NULL
MatchData$Link <- NULL
MatchData$PlayerNum <- NULL

#add column with match outcome (which is always left player according to ATP website format)
MatchData$Outcome <- 1

```

Write data to csv with the data in the title

```{r}

date <- Sys.Date()

write.csv(MatchData, file = paste("Data_",Sys.Date(),".csv",sep=""),row.names = FALSE)

```


This webscraper extracts basic player info such as height, stance, weight, birthday etc. It also takes in their average career stats.We also built in the functionality via the url links to expand or constrain the search to certain years and numbers of players.

```{r}

  num_players = 100
  
  #gets top 1979 Players, but there isn't much data on the lower end, also takes a while to run
  #url <- 'http://www.atpworldtour.com/en/rankings/singles?rankDate=2018-03-19&rankRange=1-5000'
  
  #gets top 100 Players
  url <- paste0('http://www.atpworldtour.com/en/rankings/singles?rankDate=2018-04-02&rankRange=0-',num_players)
  
  #Reading the HTML code from the website
  player_webpage <- read_html(url)
  
  #Using CSS selectors to scrap the rankings section
  PlayerName_HTML <- html_nodes(player_webpage,"td.player-cell")
  PlayerName_text <- html_text(PlayerName_HTML)
  
  #get tags
  html_nodes(player_webpage, "tbody")
  
  t = html_nodes(player_webpage, "tbody")
  
  #t2 is a list of links from the rankings player_webpage, need to iterate through every 3 places
  t2 = html_nodes(t, "a")
  
  #create list of numbers with values every three
  #THIS IS DEPENDENT ON THE 
  listnum <- seq(1,3*num_players - 1,by = 3)
  newrow = list()
  
  PlayerCodes <- data.frame(Name = PlayerName_text)
  
  PlayerCodes$Link = 0
  
  for(x in listnum) { 
    t3 <- html_attr(t2[x],"href")
    PlayerCodes$Link[(x + 2)/3] <- t3
  }
  
  #extract code from Link
  
  PlayerCodes$Code <- 0
  
  rows <- nrow(PlayerCodes)
  for(x in 1:rows){
    string <- PlayerCodes$Link[x]
    end <- nchar(string)
    last <- end -9
    first <- end - 12
    Code <- substr(string,first,last)
    
    PlayerCodes$Code[x] <- Code
  }
  

  
  
  #Getting career stats for players function
  getdata <- function(x){
    
    url <- paste0("http://www.atpworldtour.com/en/players/name-name/",x,"/player-stats?year=2018&surfaceType=hard")
    player_webpage <- read_html(url)
    
    FirstName_HTML <- html_nodes(player_webpage,".first-name")
    FirstName_text <- html_text(FirstName_HTML)
    
    LastName_HTML <- html_nodes(player_webpage,".last-name")
    LastName_text <- html_text(LastName_HTML)
    
    Name <- paste(FirstName_text,LastName_text)
    
    Birthday_HTML <- html_nodes(player_webpage,".table-birthday-wrapper")
    Birthday_text <- html_text(Birthday_HTML)
    
    #Weight_HTML <- html_nodes(player_webpage,".table-weight-kg")
    #Weight_text <- html_text(Weight_HTML)
    
    Height_HTML <- html_nodes(player_webpage,".table-height-cm-wrapper")
    Height_text <- html_text(Height_HTML)
    
    Stance_HTML <- html_nodes(player_webpage,"td:nth-child(3) .table-value")
    Stance_text <- html_text(Stance_HTML)
    
    #singlesserving
    #using xpath as the css selector
    #Aces
    Aces_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[1]/tbody/tr[1]/td[2]')
    Aces_text <- html_text(Aces_HTML)
    
    #Double Faults
    DoubleFaults_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[1]/tbody/tr[2]/td[2]')
    DoubleFaults_text <- html_text(DoubleFaults_HTML)
    
    #First Serve
    FirstServe_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[1]/tbody/tr[3]/td[2]')
    FirstServe_text <- html_text(FirstServe_HTML)
    
    #First Serve Points Won
    FirstServeWon_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[1]/tbody/tr[4]/td[2]')
    FirstServeWon_text <- html_text(FirstServeWon_HTML)
    
    #Second Serve Points Won
    SecondServeWon_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[1]/tbody/tr[5]/td[2]')
    SecondServeWon_text <- html_text(SecondServeWon_HTML)
    
    #Break Points Faced
    BreakPointsFaced_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[1]/tbody/tr[6]/td[2]')
    BreakPointsFaced_text <- html_text(BreakPointsFaced_HTML)
    
    #Break Points Saved
    BreakPointsSaved_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[1]/tbody/tr[7]/td[2]')
    BreakPointsSaved_text <- html_text(BreakPointsSaved_HTML)
    
    #Service Games Played
    ServiceGamesPlayed_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[1]/tbody/tr[8]/td[2]')
    ServiceGamesPlayed_text <- html_text(ServiceGamesPlayed_HTML)
    
    #Service Games Won
    ServiceGamesWon_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[1]/tbody/tr[9]/td[2]')
    ServiceGamesWon_text <- html_text(ServiceGamesWon_HTML)
    
    #Total Service Points Won
    TotalServicePointsWon_HTML <- html_nodes(player_webpage,xpath = '//*[@id="MatchFactsContainer"]/table[1]/tbody/tr[10]/td[2]')
    TotalServicePointsWon_text <- html_text(TotalServicePointsWon_HTML)
    
    #singlesreturn
    #First Serve Return Points Won
    FirstServeReturnPointsWon_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[2]/tbody/tr[1]/td[2]')
    FirstServeReturnPointsWon_text <- html_text(FirstServeReturnPointsWon_HTML)
    
    #Second Serve Return Points Won
    SecondServeReturnPointsWon_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[2]/tbody/tr[2]/td[2]')
    SecondServeReturnPointsWon_text <- html_text(SecondServeReturnPointsWon_HTML)
    
    #Break Points Opportunities
    BreakPointsOpportunities_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[2]/tbody/tr[3]/td[2]')
    BreakPointsOpportunities_text <- html_text(BreakPointsOpportunities_HTML)
    
    #Break Points Converted
    BreakPointsConverted_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[2]/tbody/tr[4]/td[2]')
    BreakPointsConverted_text <- html_text(BreakPointsConverted_HTML)
    
    #Return Games Played
    ReturnGamesPlayed_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[2]/tbody/tr[5]/td[2]')
    ReturnGamesPlayed_text <- html_text(ReturnGamesPlayed_HTML)
    
    #Return Games Won
    ReturnGamesWon_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[2]/tbody/tr[6]/td[2]')
    ReturnGamesWon_text <- html_text(ReturnGamesWon_HTML)
    
    #Return Points Won
    ReturnPointsWon_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[2]/tbody/tr[7]/td[2]')
    ReturnPointsWon_text <- html_text(ReturnPointsWon_HTML)
    
    #Total Points Won
    TotalPointsWon_HTML <- html_nodes(player_webpage,xpath = '//*[@id="playerMatchFactsContainer"]/table[2]/tbody/tr[8]/td[2]')
    TotalPointsWon_text <- html_text(TotalPointsWon_HTML)
    
    return(c(Name, Birthday_text, Height_text, Stance_text, Aces_text, DoubleFaults_text, FirstServe_text, FirstServeWon_text, 
             SecondServeWon_text, BreakPointsFaced_text, BreakPointsSaved_text, ServiceGamesPlayed_text, ServiceGamesWon_text, TotalServicePointsWon_text, FirstServeReturnPointsWon_text, 
             SecondServeReturnPointsWon_text, BreakPointsOpportunities_text, BreakPointsConverted_text, ReturnGamesPlayed_text, ReturnGamesWon_text,
             ReturnPointsWon_text, TotalPointsWon_text))
  }
  result = mapply(getdata, PlayerCodes$Code)
  PlayerData = plyr::ldply(result, rbind)

  
  
  #Edit Column Names
  names(PlayerData) <- c("Code", "Name","Birthday","Height","Stance","Aces","DoubleFaults","FirstServe", "FirstServeWon", 
                         "SecondServeWon", "BreakPointsFaced", "BreakPointsSaved", "ServiceGamesPlayed", "TotalServicePointsWon", "FirstServeReturnPointsWon", 
                         "SecondServeReturnPointsWon", "BreakPointsOpportunities", "BreakPointsConverted", "ReturnGamesPlayed", "ReturnGamesWon",
                         "ReturnPointsWon", "TotalPointsWon")
  
  ## DATA CLEANING
  #Remove Parentheses around Birthday
  PlayerData$Birthday <- as.character(PlayerData$Birthday)
  for(x in 1:rows){
    PlayerData$Birthday[x] <- substr(PlayerData$Birthday[x],29,38)
  }
  
  #Remove Parentheses and "cm" from Height
  PlayerData$`Height` <- as.character(PlayerData$`Height`)
  for(x in 1:rows){
    PlayerData$`Height`[x] <- substr(PlayerData$`Height`[x],2,4)
  }
  
  #function to get rid of extra text 
  #Need to make sure percentages are accounted for
  for (x in 6:ncol(PlayerData)) {
    percent = FALSE 
    PlayerData[,x] <- as.character(PlayerData[,x])
    if (grepl('%', PlayerData[1,x])) {
      percent = TRUE
    }
    for(y in 1:rows) {
      PlayerData[y, x] <- as.numeric(gsub("([0-9]+).*$", "\\1", PlayerData[y,x]))
      
      if (percent) {
        PlayerData[y,x] <- as.numeric(PlayerData[y,x])/100
      }
    }
    
    if (percent) {
      PlayerData[,x] <- as.numeric(PlayerData[,x])
    }
  }
  
  
  #now for stance 
  PlayerData$Stance <- as.character(PlayerData$Stance)
  PlayerData$Stance <- substr(PlayerData$Stance, 3, nchar(PlayerData$Stance) - 2)
  
  
  #Change PlayerData Types of individual player PlayerData
  #most of the ones commented out are percentages, should they be treated as numerics?
  PlayerData$Name <- as.character(PlayerData$Name)
  #PlayerData$Birthday is fine as a character 
  PlayerData$`Height` <- as.numeric(PlayerData$`Height`)
  #PlayerData$Stance is fine as a factor
  PlayerData$Aces <- as.numeric(PlayerData$Aces)
  PlayerData$DoubleFaults <- as.numeric(PlayerData$DoubleFaults)
  PlayerData$BreakPointsFaced <- as.numeric(PlayerData$BreakPointsFaced)
  PlayerData$ServiceGamesPlayed <- as.numeric(PlayerData$ServiceGamesPlayed)
  PlayerData$BreakPointsOpportunities <- as.numeric(PlayerData$BreakPointsOpportunities)
  PlayerData$ReturnGamesPlayed <- as.numeric(PlayerData$ReturnGamesPlayed)

# we will leftjoin them to match data here
```


Data Retrieval in its basic form ends above.

Data cleaning Begins below
